Supporting Information : Asymmetric tail-dependence in extreme climatic events affects population-extinction risk

### 2019-08-30 SuppMat.Rmd
results edited

#-------------------------------------- plot for extreme tail dep. noise ---------------------------------------
pdf(paste(resloc,"ricker_extrisk_d0_extremenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_xleft_d0,col="red",type="b",
     ylim=c(0,1),xlim = range(ricker_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025xleft,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975xleft,
       angle=90,length=0.1,col="red",code=3)
abline(v=rc_ricker,lty="dotted",col="darkgrey") #rc=1

@@

#-------------------------------------- plot for moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"ricker_extrisk_d0_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_mleft_d0,col="red",type="b",
     ylim=c(0,1),xlim = range(ricker_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025mleft,x1=ricker_extrisk_d0$r,
       y1=ricker_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_ricker,lty="dotted",col="darkgrey") #rc=1

@@

pdf(paste(resloc,"hassell_extrisk_d0_extremenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_xleft_d0,col="red",type="b",ylim=c(0,1),xlim = range(hassell_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025xleft,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975xleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted",col="darkgrey")

@@

pdf(paste(resloc,"hassell_extrisk_d0_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_mleft_d0,col="red",type="b",ylim=c(0,1),xlim = range(hassell_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025mleft,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted",col="darkgrey")

@@

pdf(paste(resloc,"msmith_extrisk_d0_extremenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_xleft_d0,col="red",type="b",ylim=c(0,1),xlim = range(msmith_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025xleft,
       x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975xleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_msmith,lty="dotted",col="darkgrey")

@@

pdf(paste(resloc,"msmith_extrisk_d0_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_mleft_d0,col="red",type="b",ylim=c(0,1),xlim = range(msmith_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025mleft,
       x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_msmith,lty="dotted",col="darkgrey")

@@

pdf(paste(resloc,"pennycuick_extrisk_d0_extremenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_xleft_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(pennycuick_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025xleft,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975xleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_pennycuick,lty="dotted",col="darkgrey")

@@

pdf(paste(resloc,"pennycuick_extrisk_d0_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_mleft_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(pennycuick_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025mleft,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_pennycuick,lty="dotted",col="darkgrey")

@@

pdf(paste(resloc,"verhulst_extrisk_d0_extremenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_xleft_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(verhulst_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025xleft,x1=verhulst_extrisk_d0$r,
       y1=verhulst_extrisk_d0$CI0.975xleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_verhulst,lty="dotted",col="darkgrey")

@@

pdf(paste(resloc,"verhulst_extrisk_d0_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_mleft_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(verhulst_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025mleft,x1=verhulst_extrisk_d0$r,
       y1=verhulst_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_verhulst,lty="dotted",col="darkgrey")

@@

pdf(paste(resloc,"abrewer_extrisk_d0_extremenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_xleft_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(abrewer_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025xleft,x1=abrewer_extrisk_d0$r,
       y1=abrewer_extrisk_d0$CI0.975xleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_abrewer,lty="dotted",col="darkgrey")

@@

pdf(paste(resloc,"abrewer_extrisk_d0_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_mleft_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(abrewer_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025mleft,x1=abrewer_extrisk_d0$r,
       y1=abrewer_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_abrewer,lty="dotted",col="darkgrey")

@@

<!--FIG:  summary: all nonlinear model results for global dispersion, extreme noise : extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_global_disp_extremenoise.pdf}
\caption[Extinction risk vs. dispersal rate for six density dependent metapopulation model with global dispersal.]{For each of six nonlinear density-dependence models presented in Table \ref{MT-tab_model_summary} with global dispersal, extinction risk varies as dispersion-rate ($d$) goes from $0$ to $0.5$. Last two columns represent extinction risk calculated for bifurcation parameter $(r)$ taken from under-compensatory and over-compensatory regime of deterministic model analog, respectively.\label{fig_extrisk_allmodel_globaldisp}}
\end{center}
\end{figure}

@@

<!--FIG: Ricker model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Ricker metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_ricker_risk_local_disp_scl_1_etd}}
\end{center}
\end{figure}

<!--FIG : Hassell model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Hassell metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_hassell_risk_local_disp_scl_1_etd}}
\end{center}
\end{figure}

<!--FIG: Maynard smith model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Maynard smith metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with local dispersal; 
numsims=10000, $\sigma$=0.8. \label{fig_msmith_risk_local_disp_scl_0.8_etd}}
\end{center}
\end{figure}

<!--FIG: Pennycuick model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Pennycuick metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_risk_local_disp_pennycuick_r_vary_scl_1_etd}}
\end{center}
\end{figure}

<!--FIG: Verhulst model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Verhulst metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with local dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_local_disp_verhulst_r_vary_scl_0.6_etd}}
\end{center}
\end{figure}

<!--FIG: Austin-Brewer model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Austin-Brewer metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Austin-Brewer dynamics with local dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_local_disp_abrewer_r_vary_scl_0.6_etd}}
\end{center}
\end{figure}

======================
<!--FIG: Ricker model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp_moderatenoise.pdf}\\
\caption[Effect of moderate tail-dependent environmental noises on extinction risk for Ricker metapopulation model with local dispersal.]{Effect of moderate tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_ricker_risk_local_disp_scl_1_mtd}}
\end{center}
\end{figure}

<!--FIG : Hassell model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp_moderatenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Hassell metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_hassell_risk_local_disp_scl_1_mtd}}
\end{center}
\end{figure}

<!--FIG: Maynard smith model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp_moderatenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Maynard smith metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with local dispersal; 
numsims=10000, $\sigma$=0.8. \label{fig_msmith_risk_local_disp_scl_0.8_mtd}}
\end{center}
\end{figure}

>>>>

#-------------------------------------- plot for extreme tail dep. noise ---------------------------------------
pdf(paste(resloc,"ricker_extrisk_d0_extremenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_xleft_d0,col="red",type="b",
     ylim=c(0,1),xlim = range(ricker_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025xleft,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975xleft,
       angle=90,length=0.1,col="red",code=3)
abline(v=rc_ricker,lty="dotted",col="black") #rc=1

@@

#-------------------------------------- plot for moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"ricker_extrisk_d0_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_mleft_d0,col="red",type="b",
     ylim=c(0,1),xlim = range(ricker_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025mleft,x1=ricker_extrisk_d0$r,
       y1=ricker_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_ricker,lty="dotted",col="black") #rc=1

@@

pdf(paste(resloc,"hassell_extrisk_d0_extremenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_xleft_d0,col="red",type="b",ylim=c(0,1),xlim = range(hassell_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025xleft,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975xleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted",col="black")

@@

pdf(paste(resloc,"hassell_extrisk_d0_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_mleft_d0,col="red",type="b",ylim=c(0,1),xlim = range(hassell_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025mleft,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted",col="black")

@@

pdf(paste(resloc,"msmith_extrisk_d0_extremenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_xleft_d0,col="red",type="b",ylim=c(0,1),xlim = range(msmith_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025xleft,
       x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975xleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_msmith,lty="dotted",col="black")

@@

pdf(paste(resloc,"msmith_extrisk_d0_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_mleft_d0,col="red",type="b",ylim=c(0,1),xlim = range(msmith_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025mleft,
       x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_msmith,lty="dotted",col="black")

@@

pdf(paste(resloc,"pennycuick_extrisk_d0_extremenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_xleft_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(pennycuick_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025xleft,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975xleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_pennycuick,lty="dotted",col="black")

@@

pdf(paste(resloc,"pennycuick_extrisk_d0_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_mleft_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(pennycuick_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025mleft,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_pennycuick,lty="dotted",col="black")

@@

pdf(paste(resloc,"verhulst_extrisk_d0_extremenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_xleft_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(verhulst_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025xleft,x1=verhulst_extrisk_d0$r,
       y1=verhulst_extrisk_d0$CI0.975xleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_verhulst,lty="dotted",col="black")

@@

pdf(paste(resloc,"verhulst_extrisk_d0_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_mleft_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(verhulst_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025mleft,x1=verhulst_extrisk_d0$r,
       y1=verhulst_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_verhulst,lty="dotted",col="black")

@@

pdf(paste(resloc,"abrewer_extrisk_d0_extremenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_xleft_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(abrewer_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025xleft,x1=abrewer_extrisk_d0$r,
       y1=abrewer_extrisk_d0$CI0.975xleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_abrewer,lty="dotted",col="black")

@@

pdf(paste(resloc,"abrewer_extrisk_d0_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_mleft_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(abrewer_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025mleft,x1=abrewer_extrisk_d0$r,
       y1=abrewer_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_abrewer,lty="dotted",col="black")

@@

<!--FIG:  summary: all nonlinear model results for global dispersion, extreme noise : extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_global_disp_extremenoise.pdf}
\caption[Extinction risk vs. dispersal rate for six density dependent metapopulation model with global dispersal.]{For each of six nonlinear density-dependence models presented in Table \ref{MT-tab_model_summary} with global dispersal, extinction risk varies as dispersion-rate ($d$) goes from $0$ to $0.5$. Last two columns represent extinction risk calculated for bifurcation parameter $(r)$ taken from under-compensatory and over-compensatory regime of deterministic model analog, respectively.\label{fig_extrisk_allmodel_globaldisp_etd}}
\end{center}
\end{figure}

@@

<!--FIG: Ricker model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Ricker metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with local dispersal; 
standard deviation $\sigma$=1 was used to generate extreme extreme tail dependent noises for 10000 simulations. \label{fig_ricker_risk_local_disp_scl_1_etd}}
\end{center}
\end{figure}

<!--FIG : Hassell model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Hassell metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with local dispersal; 
standard deviation $\sigma$=1 was used to generate extreme tail dependent noises for 10000 simulations. \label{fig_hassell_risk_local_disp_scl_1_etd}}
\end{center}
\end{figure}

<!--FIG: Maynard smith model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Maynard smith metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with local dispersal; 
standard deviation $\sigma$=0.8 was used to generate extreme tail dependent noises for 10000 simulations.. \label{fig_msmith_risk_local_disp_scl_0.8_etd}}
\end{center}
\end{figure}

<!--FIG: Pennycuick model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Pennycuick metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with local dispersal; 
standard deviation $\sigma$=1 was used to generate extreme tail dependent noises for 10000 simulations. \label{fig_risk_local_disp_pennycuick_r_vary_scl_1_etd}}
\end{center}
\end{figure}

<!--FIG: Verhulst model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Verhulst metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with local dispersal; 
standard deviation $\sigma$=0.6 was used to generate extreme tail dependent noises for 10000 simulations. \label{fig_risk_local_disp_verhulst_r_vary_scl_0.6_etd}}
\end{center}
\end{figure}

<!--FIG: Austin-Brewer model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Austin-Brewer metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Austin-Brewer dynamics with local dispersal; 
standard deviation $\sigma$=0.6 was used to generate extreme tail dependent noises for 10000 simulations. \label{fig_risk_local_disp_abrewer_r_vary_scl_0.6_etd}}
\end{center}
\end{figure}

<!--FIG: Ricker model, local dispersal, moderate noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp_moderatenoise.pdf}\\
\caption[Effect of moderate tail-dependent environmental noises on extinction risk for Ricker metapopulation model with local dispersal.]{Analogous figure as of Fig. \ref{fig_ricker_risk_local_disp_scl_1_etd} but with moderate left- and right-tail dependent noises; Moderate left tail dependence (or right tail dependence) was generated by Clayton (or Survival Clayton) copula with Kendall correlation coefficient = 0.6 between any two out of $n=5$ patches. \label{fig_ricker_risk_local_disp_scl_1_mtd}}
\end{center}
\end{figure}

<!--FIG : Hassell model, local dispersal, moderate noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp_moderatenoise.pdf}\\
\caption[Effect of moderate tail-dependent environmental noises on extinction risk for Hassell metapopulation model with local dispersal.]{Analogous figure as of Fig. \ref{fig_hassell_risk_local_disp_scl_1_etd} but with moderate left- and right-tail dependent noises; Moderate left tail dependence (or right tail dependence) was generated by Clayton (or Survival Clayton) copula with Kendall correlation coefficient = 0.6 between any two out of $n=5$ patches. \label{fig_hassell_risk_local_disp_scl_1_mtd}}
\end{center}
\end{figure}
